Quantitative Benchmarking for Automatically Generated Conjectures

### 2017-11-23 TEBenchmarkPaper/article.tex
Text additions

We applied our sampling methodology to the 269 TIP definitions for sample sizes
between 1 and 20, above which point QuickSpec becomes very slow. We chose 30
samples for each size, but the smaller sizes included repetitions due to the
requirement for samples to admit at least one theorem. A timeout of 3 minutes
was imposed, since preliminary experiments showed that most runs either finish
before this time, or still do not finish after an hour. The results are shown in
figure~\ref{figure:quickspec_results}.

@@

We are assuming that the ATE system acts in ``batch mode'' (accepting
definitions, producing conjectures, then halting), rather than running
continuously or interactively. This holds for all of the systems we have
analysed

@@

>>>>

We applied our sampling methodology to the 269 TIP definitions for sample sizes
between 1 and 20. We chose 30 samples for each size, but due to the requirement
for samples to admit at least one theorem, only 14 unique samples were obtained
for size 1 and 29 for size 2. A timeout of 3 minutes was imposed, since
preliminary experiments showed that most runs (around $\frac{4}{5}$) either
finish before this time, or still do not finish after an hour. The results are
shown in figure~\ref{figure:quickspec_results}.

The only errors we encountered were timeouts, and these occurred for all sample
sizes. Whilst the median runtimes are mostly in the range of a few seconds, the
variance increased dramatically towards size 10, and $\frac{1}{4}$ of sample
size 13 timed out.

Most runs finished quickly and generated few conjectures, with the most being
131 conjectures from a sample of size 20. Sizes 15 to 20 show a slight but
consistent reduction in runtimes, which is likely an artefact of our testing
setup.

@@

The key to our benchmarking methodology is the simplifying assumption that
theorem proving problem sets are a good proxy for desirable ATE output. This
allows us to side-step the philosophical quagmire of ``interestingness'' to
produce concrete, measurable values; it is also a core weakness, as there are
compelling reasons to refute it.

We do not claim that the use of such corpora exactly captures all interesting
conjectures of their definitions, or that those definitions exactly represent
all theories we may wish to explore. Rather, we consider our approach to offer a
pareto-optimal balance between theoretical rigour and experimental practicality,
at least in the short term.

If ATE matures to the point of providing \emph{novel} insights, even in
well-studied domains, our assumption breaks down because such results cannot (by
definition) appear in any existing corpus.

@@

\subsection{Technical Difficulties}

Our benchmarking approach only applies to systems which act in ``batch mode'',
i.e. those which choose to halt after emitting some output. Whilst all of the
systems we have encountered are of this form, an analogous benchmark may be
desirable for systems which instead run continuously or interactively (perhaps
akin to McCarthy's ``advice taker''%FIXME~\cite{}.
